Automated Topic Naming

### 2011-08-29 ese/ese.tex
updated unsup numbers for PGSQL based on exp2/3

\todo{this discussion is about which DB?}
For \textsf{exp1} the labels with the most topics

@@

%\todo[inline]{where is exp1 report?}

%EXP1 could not be evaluated properly!

@@

% 0.177215189873 / 6

@@

% EXP2 source is naming-paper/src/validate/exp2.maxdb.report.txt

@@

For \textsf{exp2}, the average F-measure (macro-F1) for MaxDB was $0.24$ with a range $0.091$ to

$0.37$, and $0.16$ for MySQL with a range of $0$ to $0.41$.

MaxDB had an average precision and recall of $0.25$ and $0.22$

while MySQL had $0.41$ and $0.10$ respectively.

@@

$0.47$, and $0.36$ for MySQL with a range of $0.10$ to $0.65$.

MaxDB had an average precision and recall of $0.16$ and $0.67$

while MySQL had $0.3$ and $0.48$ respectively.

Thus we find that \emph{reliability} and

@@

but other qualities such as \emph{functionality} did improve.

Many ROC scores were $0.6$ or less, but our classifier still performed substantially better than random.

>>>>

\todo{this discussion is about which DB? where do the #s come from?}
For \textsf{exp1} the labels with the most topics

@@

@@

\todo{update these numbers but from where? }
% 0.177215189873 / 6

@@

% EXP2 source is latest-reports/exp2-unsup-results.xls. Numbers reflect latest runs as of 08/2011.

@@

% column format is determined by info-theory.py : accuracy	f1	fn	fp	mcc	precisions	recall	roca	tn	tnr	tp
For \textsf{exp2}, the average F-measure (macro-F1) for MaxDB was  $0.24$ with a range $0.091$ to

$0.37$, and $0.16$ for MySQL with a range of $0$ to $0.41$. PostgreSQL had an average F-measure of $0.30$ %using pgsqln
 with a range of $0.09$ to $0.38$.
MaxDB had an average precision and recall of $0.25$ and $0.22$

while MySQL had $0.41$ and $0.10$ and PostgreSQL $0.31$ and $0.29$, respectively.

@@

$0.47$, and $0.36$ for MySQL with a range of $0.10$ to $0.65$. 
PostgreSQL had an average of $0.42$ with a range of $0.31$ to $0.54$.
MaxDB had an average precision and recall of $0.16$ and $0.67$

while MySQL had $0.3$ and $0.48$. PostgreSQL had precision and recall of $0.27$ and $0.95$, respectively.

Based on this we found that \emph{reliability} and

@@

but other qualities such as \emph{functionality} did improve. 
For PostgreSQL in \textsf{exp2}, \emph{reliability} and \emph{efficiency} were likewise the most accurate,
while \emph{functionality} remained poor. \emph{Functionality} improved dramatically by \textsf{exp3}.
Many ROC scores were $0.6$ or less, but our classifier still performed substantially better than random.
